---
title: "USCS Prep Sample for Qualtrics 2"
output:
  html_document:
    df_print: paged
editor_options:
  markdown:
    wrap: 75
---

### Notes

-   Assigns Weighting Segments

-   Creates New Variables

-   Writes the 'All Sample' file


```{r Load in Packages, message=F, warning=F}
if (!require("pacman")) install.packages("pacman")

# Loads in necessary packages, and installs them if you don't have them installed
pacman::p_load("tidyverse",
               "readxl",
               "stringi",
               "lubridate",
               "varhandle",
               "crfsuite")

source('Config_and_Helpers.R')

options(scipen = 9999,# Remove scientific notation
        dplyr.summarise.inform = FALSE)

knitr::opts_chunk$set(results = "asis",
                      echo=TRUE)
```

**THE FOLLOWING CHUNK DOES NOT NEED TO BE RUN IF YOU JUST RAN STEP 1 AND STILL HAVE THE 'USCS_Main' AND 'USCS_Augment' DATAFRAMES IN YOUR ENVIRONMENT**
```{r}
# Load in the generated data sets from the first step (main and augment)
load(f_str("../Data/unweighted_samples_{MONTH}_{YEAR}.Rdata"))
```

```{r message=F}
# Combine main and augment samples
USCS_Combined <- full_join(USCS_Main, USCS_Augment)
```


### AssIGNING WEIGHTING SEGMENTS

#### Dynamically establish weighting conditions

- This chunk takes in the information from the target weight summary
- It automatically extracts the conditions for the weighting segments
- An example is 
  - If sp_code = 130 & tenure_var $\geq$ 241 & account_spend $\geq$ 1500 THEN weighting_segment='SP103HTHS'
  
```{r WEIGHTING CONDITIONS}
# Load in weighting conditions
weight_conditions <- read_excel(SAMPLE_PREP_PATH,
                      sheet = "Weighting_Segments",
                      na = c("", "n/a")) %>% 
  # Drop empty rows
  drop_na(sp_code) %>% 
  # Drop unused columns
  select(-starts_with("X"))

weight_conditions <- weight_conditions %>% 
  # We first need to extract the sp codes (which are 3 digit numbers)
  # This extracts the sp codes into a list to account for if there are multiple codes associated with a single weighting segment
  mutate(sp_code = if_else(str_detect(sp_code, "[0-9]{3}"), 
                           str_extract_all(sp_code, "\\b[0-9]{3}(?![a-zA-Z])\\b"),
                           as.list(NA_character_))) %>% 
  
  # Extract tenure and spend conditions from excel's format
  mutate(
        # The tenure variable either looks like
            # NUM days+
            # NUM mos+
            # tenure < NUM mos
            # NUM1 to <NUM2 mos
            # Num1 to NUM2 mos
        # So we need to account for all cases
        tenure_var = if_else(str_detect(tenure, "days"), 
                              # If this is the days case. then divide by 30 and round up
                              ceiling(parse_number(tenure)/ 30) %>% as.character(),
                              # If not, extract all numbers (NUM or NUM1 and NUM2)
                              map_chr(str_extract_all(tenure, "[0-9]+"), ~ str_c(.x, collapse=","))),
         
        # The spend variable only has one number but can be of the form
            # $NUM+
            # <$NUM
        account_spend = parse_number(spend), # This extracts just the number
         
        # Here we determine if there was a < or + indicating whether 
          # we are looking at values less than or greater than the number
        tenure_sign = case_when(str_detect(tenure, "\\+") ~ ">=",
                                str_detect(tenure, "\\<") ~ "<",
                                TRUE ~ NA_character_), 
        spend_sign = case_when(str_detect(spend, "\\+") ~ ">=",
                                 str_detect(spend, "\\<") ~ "<",
                                 TRUE ~ NA_character_)) %>% 
  
  # Create all the conditions from the information in the excel
  mutate(
        # Now we create the tenure condition
        # This looks like 
            # NUM1 <= tenure_var  & tenure_var >= NUM2
            # NUM < tenure_var ETC
        tenure_cond = case_when(is.na(tenure) ~ NA_character_,
                                # in this case, there is NUM1 and NUM2
                                str_detect(tenure_var, ",") ~ paste(get_first_num(tenure_var),
                                                                    " <= tenure_var & tenure_var ", 
                                                                    # This is where we determine if 
                                                                    # the condition is NUM1 to <NUM2 or NUM1 to NUM2
                                                                    if_else(is.na(tenure_sign),
                                                                            "<=",
                                                                            tenure_sign),
                                                                    get_last_num(tenure_var)),
                                # This case is one NUM and we just incorporate the sign we extracted
                                TRUE ~ paste("tenure_var", tenure_sign, tenure_var)),
        
        # Here we create the spend condition which just uses the extracted sign
        spend_cond = if_else(is.na(spend), 
                             NA_character_,
                             paste("account_spend", spend_sign, account_spend)),
         # get the sp code condition
        sp_cond = if_else(is.na(sp_code),
                          NA_character_,
                          # This just creates the conditions when there are multiple codes
                          sapply(sp_code, function(x) paste0("sp_code %in% c(", paste(x, collapse = ","), ")"))),
         
        # Augmented cell condition
        naw_cond = if_else(is.na(naw_cell_code),
                           NA_character_,
                           paste0("naw_cell_code ==", "'", naw_cell_code, "'"))) %>% 
  
  # we need to properly order the conditions so ones that overlap work properly
  mutate(
        ordering = case_when(str_detect(weighting_segment, "^TX")  ~ 1,
                             str_detect(weighting_segment, "^ZX")  ~ 2,
                             str_detect(weighting_segment, "^AUG") ~ 3,
                             str_detect(weighting_segment, "^ET")  ~ 4,
                             !str_detect(weighting_segment, "SP")  ~ 5,
                             TRUE ~ 6)) %>% 
  # Create the full condition by bringing together all conditions
  unite(col = 'full_cond', sp_cond, tenure_cond, spend_cond, naw_cond, 
        sep = " & ", na.rm=TRUE) %>% # Removes any conditions that are not relevant to the given segment
  mutate(full_cond = glue("{full_cond} ~ '{weighting_segment}'")) %>% 
  arrange(ordering) %>% 
  # 
  dplyr::select(weighting_segment, 
                sp_code, 
                naw_cell_code, 
                tenure, spend, 
                full_cond)
```


 
```{r}
#  Apply the weighting conditions and generate the segments
# This is taken all those conditions we generated in the previous chunk and put them together into a case when
USCS_Weighted <- USCS_Combined %>% 
  mutate(weighting_segment = case_when(!!!rlang::parse_exprs(weight_conditions$full_cond)))
```

- Verify splits were done correctly

```{r}
# Summary Stats by weighted segment
weight_tab <- USCS_Weighted %>% 
  group_by(weighting_segment) %>%
  summarize(sp_codes = paste(unique(marketer_code), collapse = ","),
            n = n(),
            mean_spend = mean(account_spend),
            sd_spend = sd(account_spend),
            min_spend = min(account_spend),
            max_spend = max(account_spend),
            mean_tenure = mean(tenure_var),
            sd_tenure = sd(tenure_var),
            min_tenure = min(tenure_var),
            max_tenure = max(tenure_var)) %>% 
  mutate_if(is.numeric, round, digits=2) %>% 
  make_nice_table("Weighting Segments Summary Table")

# Cross-tabulation of naw_cell_code, weighting_segment, and spcode
weights_ncc_sp_code <- USCS_Weighted %>%
  freq_table(c('naw_cell_code', 'weighting_segment', 'sp_code'), 
             "Cross-tab of naw_cell_code, weighting_segment, and sp_code")

# MAKE SURE ALL OBSERVATIONS HAVE A WEIGHTING SEGMENT
# IF NOT, IDENTIFY WHAT HAPPENED IN JIM'S WEIGHTING FILE
unweighted <- weight_tab %>% filter(is.na(weighting_segment))
if (nrow(unweighted) > 0){
  warning("There are observations that fall into no weighting segment category. THIS SHOULD NOT HAPPEN")
  unweighted_sum <- unweighted %>% make_nice_table("UNWEIGHTED OBSERVATIONS")
}
```

#### Create New Variables

```{r NEW VARIABLES}
USCS_New_Vars <- USCS_Weighted %>%
  mutate(
    # Updated December 2023 to have "NULL" as default
    sv_augment_cell = if_else(naw_type == 'AUGMENT', 
                            str_extract(naw_cell_code, "[0-9]{2}"), "NULL"),
    sv_spend = case_when(
      spend == "A" ~ 1,
      spend == "B" ~ 2,
      spend == "C" ~ 3,
      spend == "D" ~ 4,
      spend == "E" ~ 5,
      spend == "F" ~ 6,
      spend == "G" ~ 7,
      spend == "H" ~ 8,
      spend == "I" ~ 9,
      spend == "J" ~ 10),
    
    bf_fico_range = ifelse(fico_range == "", "",
                           parse_number(fico_range)),
    
    bf_st_exp_enroll_in = case_when(
      st_exp_enroll_in == "C" ~ "1",
      st_exp_enroll_in == "E" ~ "2",
      st_exp_enroll_in == "H" ~ "3",
      st_exp_enroll_in == "I" ~ "4",
      st_exp_enroll_in == "N" ~ "5",
      st_exp_enroll_in == "O" ~ "6",
      st_exp_enroll_in == "R" ~ "7",
      st_exp_enroll_in == "S" ~ "8",
      st_exp_enroll_in == "X" ~ "9",
      st_exp_enroll_in == "P" ~ "10",
      st_exp_enroll_in == "" ~ "",
      TRUE ~ "REF"),
    
    
    bf_expo_enroll_in = case_when(
      expo_enroll_in == "C" ~ "1",
      expo_enroll_in == "E" ~ "2",
      expo_enroll_in == "H" ~ "3",
      expo_enroll_in == "I" ~ "4",
      expo_enroll_in == "N" ~ "5",
      expo_enroll_in == "O" ~ "6",
      expo_enroll_in == "R" ~ "7",
      expo_enroll_in == "S" ~ "8",
      expo_enroll_in == "X" ~ "9",
      expo_enroll_in == "P" ~ "10",
      expo_enroll_in == "" ~ "",
      TRUE ~ "REF"),
    
    bf_myca_flg = case_when(
      myca_flag == "" ~ "",
      myca_flag == "Y" ~ "1",
      myca_flag == "N" ~ "2",
      TRUE ~ "R"), # This should be REF but SAS cut it short so Qualtrics expects an R
    
    bf_mr_in = case_when(mr_in == "" ~ "",
                         mr_in == "Y" ~ "1",
                         mr_in == "N" ~ "2",
                         TRUE ~ "REF"),
    
    bf_purch_apr_rt = case_when(
      purch_apr_rt > 0 ~ round(purch_apr_rt,2) %>% as.character(),
      purch_apr_rt == -1 ~ "",
      TRUE ~ "REF"),
    
    # /**********CHECK TENURE*************/
    cv_cs_et_type = case_when(
      # Ops asked that SP code 158, new in Jan 2023, be called early tenure 
      # even though tenure_var values exceed 4 see email from Hunter 1/3/23*/
      #marketer_code == "SP158" ~ 1, # Removed Q1 2023 
      tenure_var >= 2 & tenure_var <= 4  ~ 1,
      tenure_var >= 5 & tenure_var <= 15 ~ 2,
      TRUE ~ 3),
    
    
    #/*N_User_id=length(Personalization1)-1, userid=SUBSTR(Personalization1,2,N_User_id), #*/*per Brent 1/9/2018,
    survey_type = "USCS",
    #*Need to be exact,
    country = "United States",
    #*Need to be exact,
    country_code = 90,
    language = "EN",
    #*Need to be exact-"Language",
    
    #*CV_PORTFOLIO,
    cv_portfolio = case_when(
      marketer_code %in%  c('SP101',
                            'SP149',
                            'SP148',
                            'SP103',
                            'SP105',
                            'SP106',
                            'SP150',
                            'SP151',
                            'SP108',
                            'SP110',
                            'SP117',
                            'SP120',
                            'SP135'
                          ) ~ 1,
      
      marketer_code %in%  c('SP111',
                            'SP112',
                            'SP113',
                            'SP114',
                            'SP115',
                            'SP118',
                            'SP132',
                            'SP133',
                            'SP145',
                            'SP146',
                            'SP156'
                          ) ~ 2,
      
      marketer_code %in%  c('SP123',
                            'SP124',
                            'SP125',
                            'SP126',
                            'SP127',
                            'SP129',
                            'SP130',
                            'SP136',
                            'SP137',
                            'SP138',
                            'SP139',
                            'SP142',
                            'SP153',
                            'SP154',
                            'SP155',
                            'SP157',
                            'SP158'
                          ) ~ 3),
    
    #/*USE SMART_REV for Weighting Segment because CV_MARKET_SIZE wasn't working;

	  #/* cyear and Month_2dig will be used to append the Weight_segment and CV_interview_data variables.
	  #   note that cyear and cmonth are initizlized in step1*/
    
    month_2dig = formatC(MONTH_NO, width = 2, flag = "0"),
    cv_interview_date = paste0(YEAR, month_2dig),
    weighting_segment_nu = paste0(weighting_segment, cv_interview_date),
  
    best_dma = ifelse(best_dma_cd == 0 |
                      best_dma_cd == 999 |
                      is.na(best_dma_cd),
                      "REF",
                       as.character(best_dma_cd)),
       
    #card anniversary date
    card_anniv_dt = if_else(card_anniv_dt == "0001-01-01",
                            NA_character_, card_anniv_dt),
    anniv = as_date(card_anniv_dt, format = "%Y-%m-%d"),
    bf_card_anniv_year = year(anniv),
    bf_card_anniv_month = month(anniv),
       
    # Card setup date
    setup_dt = if_else(setup_dt == "0001-01-01",
                       NA_character_, setup_dt),
    setup = as_date(setup_dt, format = "%Y-%m-%d"),
    bf_setup_year = year(setup),
    bf_setup_month = month(setup),
    bf_setup_day = day(setup),
       
    # Prog Enter Date
    mr_init_enroll_dt = if_else(mr_init_enroll_dt == "0001-01-01",
                            NA_character_, mr_init_enroll_dt),
    enrolls = as_date(mr_init_enroll_dt, format = "%Y-%m-%d"),
    bf_mr_init_enroll_year = year(enrolls),
    bf_mr_init_enroll_month = month(enrolls),
    bf_mr_init_enroll_day = day(enrolls),
       
    #*AGE;
    dInterviewDate = YEAR + (MONTH_NO/12),
    dYOB = floor(dInterviewDate-raw_age),
    year_of_birth = ifelse(is.na(raw_age) | 
                           dYOB < 1850 | 
                           dYOB > (year(Sys.Date()) - 17), 
                           "", 
                           as.character(dYOB)),
  
    generation =case_when(year_of_birth == "" ~ "",
                           dYOB < 1946 ~ "Silent: 1945 and prior",
                           dYOB < 1965 ~ "Baby Boomers: 1946 - 1964",
                           dYOB < 1980 ~ "Generation X: 1965 - 1979",
                           dYOB < 1989 ~ "Older Millennials: 1980 - 1988",
                           dYOB < 1997 ~ "Younger Millennials: 1989 - 1996",
                           dYOB >= 1997 ~ "Generation Z: 1997 and later"),
  
    bdl_fico_bucket = case_when(is.na(raw_fico) | raw_fico == -1 ~ "",
                                raw_fico < 650 ~ "1",
                                raw_fico < 720 ~ "2",
                                raw_fico >= 720 ~ "3"),
  
    cv_amex_has_fee = case_when(marketer_code %in% c("SP101", "SP103", "SP105", 
                                                     "SP106", "SP108", "SP110", 
                                                     "SP120", "SP124", "SP125", 
                                                     "SP126", "SP129", "SP130", 
                                                     "SP133", "SP135", "SP137", 
                                                     "SP138", "SP139", "SP142", 
                                                     "SP146", "SP148", "SP149", 
                                                     "SP150", "SP151", "SP154", 
                                                     "SP155", "SP157", "SP158") ~ "1",
                                
                                marketer_code %in% c("SP111", "SP112", "SP113", 
                                                     "SP114", "SP115", "SP117", 
                                                     "SP118", "SP123", "SP127", 
                                                     "SP132", "SP136", "SP145", 
                                                     "SP153", "SP156") ~ "2",
                                TRUE ~ "REF"),
  
    account_spend = ifelse(is.na(account_spend), 0, account_spend),
    
    cv_mr_category = case_when(mr_tier_prog_cd == "PR" ~ 1,
                               mr_tier_prog_cd == "MR" ~ 2,
                               mr_tier_prog_cd == "LF" ~ 3,
                               TRUE ~ NA_real_),
    
    cv_augment_sample = ifelse(naw_cell_code %in% c("CELL18", "CELL21", "CELL22", 
                                                   "CELL14", "CELL35", "CELL53",
                                                   "CELL54", "CELL55", "CELL56",
                                                   "CELL57", "CELL58", "CELL59",
                                                   "CELL60", "CELL61", "CELL62", 
                                                   "CELL66"),
                               1,
                               2),
    account_share_of_wallet = ifelse(size_of_wallet != 0, 
                                     account_spend / size_of_wallet, 
                                     NA),  
    
    card_name =case_when(marketer_code == 'SP101' ~ 'Platinum',
                         marketer_code == 'SP103' ~ 'Gold Charge No Rewards',
                         marketer_code == 'SP105' ~ 'Gold',
                         marketer_code == 'SP106' ~ 'Senior Gold',
                         marketer_code == 'SP108' ~ 'Green Charge No Rewards',
                         marketer_code == 'SP110' ~ 'Senior Green',
                         marketer_code == 'SP111' ~ 'Platinum, Platinum Preferred, Gold Optima',
                         marketer_code == 'SP112' ~ 'Standard and Classic Optima',
                         marketer_code == 'SP113' ~ 'Blue',
                         marketer_code == 'SP114' ~ 'Blue Cash',
                         marketer_code == 'SP115' ~ 'BlueSky',
                         marketer_code == 'SP117' ~ 'One',
                         marketer_code == 'SP118' ~ 'Clear',
                         marketer_code == 'SP119' ~ 'Cash Rebate',
                         marketer_code == 'SP120' ~ 'Zync',
                         marketer_code == 'SP123' ~ 'Hilton Honors',
                         marketer_code == 'SP124' ~ 'Hilton Honors Surpass',
                         marketer_code == 'SP125' ~ 'Delta Gold',
                         marketer_code == 'SP126' ~ 'Delta Platinum',
                         marketer_code == 'SP127' ~ 'Delta Blue',
                         marketer_code == 'SP128' ~ 'Delta Classic & SkyPoints',
                         marketer_code == 'SP129' ~ 'Delta Reserve',
                         marketer_code == 'SP130' ~ 'Marriott Bonvoy',
                         marketer_code == 'SP132' ~ 'Blue Cash Everyday',
                         marketer_code == 'SP133' ~ 'Blue Cash Preferred',
                         marketer_code == 'SP134' ~ 'Blue Sky Preferred',
                         marketer_code == 'SP135' ~ 'Centurion',
                         marketer_code == 'SP136' ~ 'Morgan Stanley Credit',
                         marketer_code == 'SP137' ~ 'Morgan Stanley Platinum',
                         marketer_code == 'SP138' ~ 'Ameriprise Gold',
                         marketer_code == 'SP139' ~ 'Ameriprise Platinum',
                         marketer_code == 'SP140' ~ 'Fidelity Platinum',
                         marketer_code == 'SP141' ~ 'Fidelity Gold',
                         marketer_code == 'SP142' ~ 'Goldman Sachs Platinum',
                         marketer_code == 'SP143' ~ 'Mercedes-Benz Credit',
                         marketer_code == 'SP144' ~ 'Mercedes-Benz Platinum',
                         marketer_code == 'SP145' ~ 'Amex EveryDay',
                         marketer_code == 'SP146' ~ 'Amex EveryDay Preferred',
                         marketer_code == 'SP148' ~ 'Traditional Gold with Rewards',
                         marketer_code == 'SP149' ~ 'Classic Gold',
                         marketer_code == 'SP150' ~ 'Green',
                         marketer_code == 'SP151' ~ 'Traditional Green with Rewards',
                         marketer_code == 'SP152' ~ 'Plenti',
                         marketer_code == 'SP153' ~ 'Schwab Investor',
                         marketer_code == 'SP154' ~ 'Schwab Platinum',
                         marketer_code == 'SP155' ~ 'Hilton Honors Aspire',
                         marketer_code == 'SP156' ~ 'Cash Magnet',
                         marketer_code == 'SP157' ~ 'Marriott Bonvoy Brilliant',
                         marketer_code == 'SP158' ~ 'Marriott Bonvoy Bevy'),
    
    # Set to an empty variable. Use to come from a file that has not been updated in a long time
    CCSG_CENTURION_TIER = ""
    )
```

### CHECKS FOR NEW VARIABLES

- Most of these need to be hand checked since they were created by the same formulas that would be used to check their correctness

```{r}
fico <- table(USCS_New_Vars$fico_range, USCS_New_Vars$bf_fico_range, useNA = "ifany") %>% make_nice_table("FICO Range vs BF FICO Range")
enroll <- table(USCS_New_Vars$st_exp_enroll_in, USCS_New_Vars$bf_st_exp_enroll_in, useNA = "ifany") %>% make_nice_table("st_exp_enroll_in vs bf_st_exp_enroll_in")
myca_flag <- table(USCS_New_Vars$myca_flag, USCS_New_Vars$bf_myca_flg, useNA = "ifany") %>% make_nice_table("myca_flag vs bf_myca_flg")
mr_in <- table(USCS_New_Vars$mr_in, USCS_New_Vars$bf_mr_in, useNA = "ifany") %>% make_nice_table("mr_in vs BF_mr_in")


cv_et <- USCS_New_Vars %>% group_by_summary_table("cv_cs_et_type", "tenure_var") # *1 = tenure < 5, 2=tenure 5-15, 3=tenure > 15;

no_cv_cs_et <- USCS_New_Vars %>% filter(is.na(cv_cs_et_type)) 

if (nrow(no_cv_cs_et) > 0) warning("Missing CV CS ET Type")


port_mc <- table(USCS_New_Vars$marketer_code, USCS_New_Vars$cv_portfolio, useNA = "ifany") %>% make_nice_table("cv_portfolio vs marketer_code")
fee_mc <- table(USCS_New_Vars$marketer_code, USCS_New_Vars$cv_amex_has_fee, useNA = "ifany") %>% make_nice_table("cv_amex_has_fee vs marketer_code")

if (sum(is.na(USCS_New_Vars$account_number)) > 0) warning("Missing account spend found")

tier_cat <- table(USCS_New_Vars$mr_tier_prog_cd, USCS_New_Vars$cv_mr_category, useNA = "ifany") %>% 
  make_nice_table("mr_tier_prog_cd vs cv_mr_category")
aug_naw <- table(USCS_New_Vars$cv_augment_sample, USCS_New_Vars$naw_cell_code, useNA = "ifany") %>% 
  make_nice_table("cv_augment_sample vs naw_cell_code")


if(USCS_New_Vars %>% 
   filter(replace_na(best_dma_cd,"") %in% c('','999','0')) %>% 
   nrow() > 0) warning("DMA_CD contains missing val, blank, 0 or 999")

if(USCS_New_Vars %>% 
   filter(replace_na(best_dma,"") %in% c('','999','0')) %>% 
   nrow() > 0) warning("DMA contains missing val, blank, 0 or 999")

yobs <- USCS_New_Vars %>% mutate(age = ceiling(raw_age)) %>% 
  distinct(dInterviewDate, dYOB, age, year_of_birth) %>%
  arrange(age) %>% 
  make_nice_table("Checking year of birth calculations") # Are ages correct

gens <- USCS_New_Vars %>% distinct(year_of_birth, generation) %>% 
  arrange(year_of_birth) %>% 
  make_nice_table("Checking Generation calculations")

fico <- USCS_New_Vars %>% distinct(raw_fico, bdl_fico_bucket) %>% 
  arrange(bdl_fico_bucket, raw_fico) %>% 
  make_nice_table("Checking FICO Bucket")
```


```{r}
# Identify people with missing first and last names
miss_name <- USCS_New_Vars %>% 
  filter(is.na(first_nm) | is.na(last_nm)) %>% 
  dplyr::select(customer_id,first_nm, last_nm)

if (nrow(miss_name) > 0){
  warning('People with missing first or last names found')
  message("These will be replaced with 'Valued Card Member'")
 miss_name %>% make_nice_table("People with Missing Names")
} else{
  message("SUCCESS: No people with missing first or last names")
}
```

```{r}
# Fill in the blank names with "Valued Card Member" because First and Last name are now included in the AllSample file
USCS_New_Vars <- USCS_New_Vars %>% 
  mutate(name_tmp = is.na(first_nm) | is.na(last_nm) | nchar(first_nm) == 10,
    first_nm = if_else(name_tmp,
                       "Valued Card",
                       first_nm),
         last_nm = if_else(name_tmp,
                          "Member",
                          last_nm))
```

```{r message=F}
# Read in Subject Line Code Info

subject_line_insert_info <- read_csv(SUBJECT_LINE_PATH) %>% 
  set_names(c('ia_id', 'sv_subject_line_insert'))
```

- check if there are records that did not match with the Subject line insert file;

```{r}
# check if there are records that did not match with the Subject line insert file
USCS_New_Vars <- USCS_New_Vars %>% 
  left_join(subject_line_insert_info, by = "ia_id")

miss_inserts <- USCS_New_Vars[is.na(USCS_New_Vars$sv_subject_line_insert),]
if(nrow(miss_inserts) > 0){
  warning("Missing subject line inserts")
  print(miss_inserts %>% dplyr::select(customer_id, sv_subject_line_insert))
} else{
  
  message("SUCCESS: No missing subject line inserts")
}
```

```{r}
ia_subline_freq <- USCS_New_Vars %>% 
  freq_table(c("ia_id", "sv_subject_line_insert"), 
             "Freq table IA ID vs Subject Line insert")
```

```{r message = F}
# Create new variable and replace empty values with "American Express Card"
USCS_New_Vars <- USCS_New_Vars %>% 
  mutate(sv_subject_line_insert = if_else(sv_subject_line_insert == "", 
                                          "American Express Card", sv_subject_line_insert))

# Read in Card Art URLs and sort data
card_art_info <- read_csv(CARD_ART_PATH) %>% 
  dplyr::select(marketer_code = `SP Code`,
                sv_card_art = SV_CARD_ART)

# Merge data
USCS_New_Vars <- USCS_New_Vars %>% left_join(card_art_info)

sp_sv_card_freq <- USCS_New_Vars %>% 
  freq_table(c("marketer_code","sv_card_art"), "SP Code vs SV Card Freq Table")
```

```{r}
# Change all date columns to "M/D/YYYY" format
USCS_New_Vars <- USCS_New_Vars %>% 
  mutate(across(c("setup_dt",
                  'card_anniv_dt',
                  'mr_init_enroll_dt'), ~format(as.Date(.x), format = "%m/%d/%Y")),
         # We need to remove leading zeros in months and days
         across(c("setup_dt",
                  'card_anniv_dt',
                  'mr_init_enroll_dt'), ~gsub("^0", "", gsub("/0", "/", .))))
```


```{r message=F}
# Merging the data frames
USCS_Final <- USCS_New_Vars %>% 
  arrange(naw_cell_code, marketer_code, spend, tenure_cat) %>% # Sort Data 
  set_names(str_to_upper(names(.))) %>% 
  # Choose only desired variables and name them how we want them named
  dplyr::select(BF_GMPI_BASE_CUST_ID = GMPI_BASE_CUST_ID,
                FIRST_NM,
                LAST_NM,
                BF_CITY_NM = CITY_NM,
                BF_STATE_TX = STATE_TX,
                BF_US_ZIP = US_ZIP,
                BF_LAST5 = LAST5,
                BF_IA_ID = IA_ID,
                BF_FMLY_DS_TX = FMLY_DS_TX,
                BF_CARD_ROLLUP_DS_TX = CARD_ROLLUP_DS_TX,
                BF_CONS_FRIENDLY_DS_TX = CONS_FRIENDLY_DS_TX,
                BF_SETUP_DT = SETUP_DT,
                BF_BEST_DMA_CD = BEST_DMA,
                BF_MAIL_ID = MAIL_ID,
                BF_CELL_CODE = CELL_CODE,
                BF_MARKETER_CODE = MARKETER_CODE,
                BF_MYCA_FLG,
                BF_MR_IN,
                BF_ACCOUNT_SPEND = ACCOUNT_SPEND,
                BF_SIZE_OF_WALLET = SIZE_OF_WALLET,
                BF_SHARE_OF_WALLET_AMEX = SHARE_OF_WALLET_AMEX,
                BF_CARD_ANNIV_DT = CARD_ANNIV_DT,
                BF_AGE_RANGE = AGE_RANGE,
                BF_CUSTOMER_SPEND = CUSTOMER_SPEND,
                BF_FICO_RANGE,
                BF_ACTIVE_SUPP_CT = ACTIVE_SUPP_CT,
                BF_ST_EXP_ENROLL_IN,
                BF_EXPO_ENROLL_IN,
                BF_MR_TIER_PROG_CD = MR_TIER_PROG_CD,
                BF_MR_INIT_ENROLL_DT = MR_INIT_ENROLL_DT,
                BF_AVLBL_PNTS = AVLBL_PNTS,
                BF_ACCT_TRANS_PNTS_NO = ACCT_TRANS_PNTS_NO,
                BF_TOT_RVLV_INT_AM = TOT_RVLV_INT_AM,
                BF_RVLV_MTHS_NO = RVLV_MTHS_NO,
                BF_TOT_LOC_INT_AM = TOT_LOC_INT_AM,
                BF_TOT_LOC_INT_MTH_NO = TOT_LOC_INT_MTH_NO,
                BF_TOT_LOC_AM = TOT_LOC_AM,
                SV_SP_CODE = SP_CODE,
                SV_AUGMENT_CELL,
                SV_STUDY_OPENEND = MV_NPS_IND,
                SV_MR_IN = MR_IN_N,
                SV_TENURE_QUANT = TENURE_VAR,
                BF_RDM_NET_12M_CT = RDM_NET_12M_CT,
                BF_LINE_OF_CREDIT_AM = LINE_OF_CREDIT_AM,
                BF_PURCH_APR_RT,
                SV_SUBJECT_LINE = SUBJECT_LINE,
                SV_PRODUCT_TENURE = T_ADD,
                WV_WEIGHTING_SEGMENT = WEIGHTING_SEGMENT_NU,
                SV_SPEND,
                SURVEY_TYPE,
                COUNTRY,
                COUNTRY_CODE,
                LANGUAGE,
                CV_PORTFOLIO,
                CV_INTERVIEW_DATE,
                CV_AMEX_HAS_FEE,
                CV_MR_CATEGORY,
                CV_CS_ET_TYPE,
                CCSG_CENTURION_TIER,
                CV_BF_ACCOUNT_SHARE_OF_WALLET = ACCOUNT_SHARE_OF_WALLET,
                BF_CARD_ANNIV_YEAR,
                BF_CARD_ANNIV_MONTH,
                BF_MR_INIT_ENROLL_YEAR,
                BF_MR_INIT_ENROLL_MONTH,
                BF_MR_INIT_ENROLL_DAY,
                BF_SETUP_YEAR,
                BF_SETUP_MONTH,
                BF_SETUP_DAY,
                CARD_NAME,
                BDL_AGE = RAW_AGE,
                BDL_FICO_SCORE = RAW_FICO,
                YEAR_OF_BIRTH,
                CV_Generation_New = GENERATION,
                BDL_FICO_BUCKET,
                SV_SUBJECT_LINE_INSERT,
                SV_CARD_ART)
```

```{r Reformatting}
# Final rounding to get the data in the format that Qualtrics is expecting
USCS_Final <- USCS_Final %>% mutate(
         BF_GMPI_BASE_CUST_ID = substr(BF_GMPI_BASE_CUST_ID, 5, 19), # We only want 15 digits
         across(c("BF_ACCOUNT_SPEND",
                  'BF_SIZE_OF_WALLET',
                  'BF_SHARE_OF_WALLET_AMEX',
                  'BF_CUSTOMER_SPEND',
                  "BDL_AGE",
                  "SV_PRODUCT_TENURE"), ~round(., 2)),
         CV_BF_ACCOUNT_SHARE_OF_WALLET = txt_sprintf("%.14f", CV_BF_ACCOUNT_SHARE_OF_WALLET),
         across(c('BF_CARD_ANNIV_DT', "BF_CARD_ANNIV_YEAR", "BF_CARD_ANNIV_MONTH",
                  'BF_SETUP_DT', 'BF_SETUP_YEAR', 'BF_SETUP_MONTH', 'BF_SETUP_DAY'), 
                ~ifelse(. == "" | is.na(.), "REF", .)) # Make missing values "REF"
)
```

```{r}
MONTH_STR <- sprintf("%02d", MONTH_NO)
USCS_Final %>% write_csv("../Files_to_send/AmexGABMUSCSSurvey_{YEAR}{MONTH_STR}_{Sys.Date()}.csv" %>% f_str(), na ="")
```

```{r}
# Store final dataset for ease of loading in formats
save(USCS_Final, file=f_str("../Data/USCS_final{MONTH}_{YEAR}.Rdata"))
```

```{r }
rm.all.but(keep=c('USCS_Final', 'MONTH', 'YEAR'))
```

```{r}
# Load final dataset for quick checks if needed
# load(f_str("../Data/USCS_final{MONTH}_{YEAR}.Rdata"))
```