---
title: "USCS Prep Sample"
output:
  html_document:
    df_print: paged
editor_options:
  markdown:
    wrap: 75
---

## Preparatory Steps

Consult `ReadMe.md` for instructions on how to configure the inputs
properly before running this script

Remember to update file paths and variables in `USCS_Config.R`

 **This code will output warnings and messages.** The warnings indicate
    a check is not met. These will be printouts with "Warning:" before
    them. If a check is passed, a message will be printed with a green "✔"
    before it. If any warnings are printed, figure out why and report if
    the warning says to. Many warning will just be for typical removals

## Dependencies

```{r Load in Packages, message=FALSE, warning=FALSE}
if (!require("pacman")) install.packages("pacman")

# Loads in necessary packages, and installs them if you don't have them installed
pacman::p_load("tidyverse",
               "stringi",
               "varhandle",
               "openxlsx",
               "cli",
               "janitor",
               "lubridate",
               "crfsuite")

# Load in configuration file variables and functions
source('USCS_Helper_Functions.R') 

options(scipen = 99999, # Remove scientific notation
        dplyr.summarise.inform = FALSE) # Remove summarize messages

knitr::opts_chunk$set(results = "asis", # Prints html tables nicely
                      echo=TRUE) # Show all code chunks in the output

# Initialize Diagnostic Workbook
Diagnostic_WB <- createWorkbook()
```

## Data Loading

- As of June 2023, we are ignoring the data that comes in from the Spend file as we do not include any of its variables in the final sample
- So disregard any anomalies with the spend dataframe
- The code may be removed for loading spend in the future

```{r Load in base and spend dataframes}
USCS_Base <- load_base() 
# USCS_Spend <- load_spend()
```

```{r Join Data}
# USCS_Sample <- inner_join(USCS_Base, USCS_Spend, by = "gmpi_base_cust_id") %>% mutate(is_main = cell_code %in% MAIN_CELL_CODES)
# 
# if (nrow(USCS_Sample) != nrow(USCS_Base)){
#   cli_abort("The BASE and SPEND datasets do not line up. Something is wrong. Ask PM if we can ignore the Spend dataset--as no variables are used from it anyway.")
# } else{
#   cli_alert_success("BASE and SPEND datasets line up.")
# }

# If ignoring SPEND, just uncomment this line instead.
USCS_Sample <- USCS_Base %>% mutate(is_main = cell_code %in% MAIN_CELL_CODES)
```

```{r Missing Value Summary}
# Variables to summarize number of missing values
# This is mostly just for logging what's happened
# just make sure no variables have a large number of missing values, in my (Beck's) 2 years, I haven't seen anything with more than 0.05% missing
miss_vars <- c("first_nm", 'last_nm',
               "raw_fico", "fico_range",
               "raw_age",
               "share_of_wallet_amex", "size_of_wallet",
               "customer_spend", "account_spend")

missing_vals <- USCS_Sample %>% count_missing(miss_vars)
```

## Checking Expected Counts

-   Compare sample requested vs count received
-   To check the counts of the main sample, we check it against the counts for the main marketer codes
-   To check the counts of the augment, we use the `Augment_Specs` sheet

```{r Check Cell Codes}
# Create a frequency table of each cell code
cell_code_freq <- USCS_Sample %>% freq_table("cell_code")  %>% 
  select(cell_code, Freq) %>% arrange(parse_number(cell_code)) %>% 
  make_nice_table(caption = "Cell Code Frequencies")

# Save to output excel file to be sent to PM
add_and_write_sheet(Diagnostic_WB, "Cell_Code_Freqs", cell_code_freq)

main_marketer_codes <- USCS_Sample %>% filter(is_main) %>% freq_table("marketer_code", caption = "Marketer Code Frequencies for Main Cell Codes")

# Write to excel to send to OPS Manager
add_and_write_sheet(Diagnostic_WB, "Main_Marketer_Code_Freqs", main_marketer_codes)
```


```{r Main Cell Code Counts Check}
# Load in expected marketer code counts
req_marketer_codes <- load_req_marketer_codes()

# Check Counts
main_marketer_codes_check <- main_marketer_codes %>% 
  left_join_suppress(req_marketer_codes) %>% select(marketer_code, count_received = Freq, count_requested) %>% 
  filter((count_received - count_requested) != 0)

log_section_start("Main Sample Marketer Code")
log_check_result(
  condition = nrow(main_marketer_codes_check) == 0,
  type = "marketer codes",
  check_type = "counts",
  data = main_marketer_codes_check,
  row_message = "{row$marketer_code}: Expected {comma(row$count_requested)} | Received {comma(row$count_received)}"
)
```

```{r Augment Cell Code Counts Check}
augment_specs <- load_augment_specs()

# Check counts
augment_cc_check <- USCS_Sample %>% filter(!is_main) %>% 
  count(cell_code, name = "count_received") %>% 
  left_join_suppress(augment_specs) %>% 
  filter((count_received - count_requested) != 0)


log_section_start("Augment Cell Code Count Check")
log_check_result(
  condition = nrow(augment_cc_check) == 0,
  type = "cell codes",
  check_type = "counts",
  data = augment_cc_check,
  row_message = "{row$cell_code}: Expected {comma(row$count_requested)} | Received {comma(row$count_received)}"
)
```

```{r Add Helper Variables}
 # Add some helper variables -- most are not included in the output
USCS_Sample <- USCS_Sample %>%
  mutate(raw_setup_dt = setup_dt,
         setup_dt = na_if(setup_dt,  "0001-01-01"),
         setup = as_date(setup_dt, format = "%Y-%m-%d"),
         
         # Official tenure in months
         tenure_var = 12 * (YEAR - 1 - year(setup)) + (MONTH_NO + 12 - month(setup)),
         
         # Tenure in days used for validation
         tenure_days = as.numeric(DATE_SAMPLE_RECIEVED - setup),
         
         customer_id = as.numeric(gmpi_base_cust_id),
         
         sp_code = parse_number(marketer_code)
         ) %>% 
         
         # perform ab split (if desired)
         # makes new variables based on split
         # The create_ab_split function will create the "selected" variable. So if you are performing the ab_split, remove the line that defaults the selected variable to 0.
  
  #create_ab_split(strat_var = 'marketer_code', sample_size = 0.5) %>% # Stratify sample 50% of obs for each marketer code
  mutate(selected = 0) %>%   # Or use create_ab_split() if needed
  mutate(
         mv_nps_ind = if_else(selected == 0, "NPS", "MV"),
         subject_line = if_else(selected == 0, 6, 7),
         
         mr_in_n = if_else(mr_in == 'Y', 1, 2)
         )
```

## Checking for Duplicate Keys

```{r Dupe Check}
# Identify duplicates for customer id and username/password
cust_id_dupes <- USCS_Sample[duplicated(USCS_Sample$gmpi_base_cust_id),]
pers_dupes <- USCS_Sample[duplicated(USCS_Sample[,c("personalization1", "personalization2")]),]

# Customer ID duplicates check
log_section_start("Customer ID")
log_check_result(
  condition = nrow(cust_id_dupes) == 0,
  type = "customer ID",
  check_type = "dupes",
  data = cust_id_dupes$gmpi_base_cust_id
)

# Username/password duplicates check
log_section_start("Username/Password")
log_check_result(
  condition = nrow(pers_dupes) == 0,
  type = "username/password",
  check_type = "dupes",
  data = pers_dupes,
  row_message = "Username: {row$personalization1}, Password: {row$personalization2}"
)
```

## DMA Frequency

-   Make sure all DMA Codes are valid using the `DMA_Checks` sheet.

```{r DMA Check}
# Load in valid dmas
valid_dmas <- load_valid_dmas()

# identify invalid dma's if any and get frequencies
invalid_dmas <- USCS_Sample %>% 
 filter(!best_dma_cd %in% valid_dmas) %>% count(best_dma_cd)

# DMA check
log_section_start("DMA Code")
log_check_result(
  condition = nrow(invalid_dmas) == 0,
  type = "DMA codes",
  check_type = "validity",
  data = invalid_dmas,
  row_message = "DMA Code {row$best_dma_cd}: {row$n} occurrences"
)
```

## Check Validity of Certain Variables for Removal
  - Account Spend
  - Tenure
  - Setup Date
  - Marketer Code
  - ' ' at start of Customer ID
  - Year of Birth:  Make sure no one is less than 18 or older than 120
  

```{r Variable Validity Checks}
cli_h1("Variable Validity Checks")
cli_alert_warning("Records with invalid values will be removed at the end of this script")

# MISSING SPEND
to_remove_miss_spend <- USCS_Sample[USCS_Sample$account_spend == "" | is.na(USCS_Sample$account_spend),]
log_check_result(
  condition = nrow(to_remove_miss_spend) == 0,
  type = "account spend",
  check_type = "missing",
  count = nrow(to_remove_miss_spend)
)

if(nrow(to_remove_miss_spend) > 0) add_and_write_sheet(Diagnostic_WB, "Removed_Missing_Spend", to_remove_miss_spend)

# MISSING TENURE
to_remove_miss_tenure <- USCS_Sample[USCS_Sample$t_add == "" | is.na(USCS_Sample$t_add),]
# Tenure check
log_check_result(
  condition = nrow(to_remove_miss_tenure) == 0,
  type = "tenure",
  check_type = "missing",
  count = nrow(to_remove_miss_tenure)
)

if(nrow(to_remove_miss_tenure) > 0) add_and_write_sheet(Diagnostic_WB, "Removed_Missing_Tenure", to_remove_miss_tenure)

# INVALID TENURE AND SPEND
to_remove_tenure_spend_helper <- USCS_Sample %>% filter(!is_main) %>% 
  select(gmpi_base_cust_id, cell_code, tenure_var, tenure_days,
                      account_spend, marketer_code, setup_dt) %>%  
  inner_join(augment_specs, by="cell_code")  %>% 
  mutate(tenure_days_max = replace_na(tenure_days_max, Inf),
         flag_tenure = tenure_days < tenure_days_min | tenure_days > tenure_days_max,
         flag_spend = (account_spend <= 0 & min_spend == ">$0")) 

## INVALID TENURE
to_remove_tenure <- to_remove_tenure_spend_helper %>% filter(flag_tenure) %>% select(-starts_with("flag"))
log_check_result(
  condition = nrow(to_remove_tenure) == 0,
  type = "augment tenure",
  check_type = "validity",
  count = nrow(to_remove_tenure)
)
if(nrow(to_remove_tenure) > 0) add_and_write_sheet(Diagnostic_WB, "Removed_Invalid_Tenure", to_remove_tenure)

## INVALID SPEND
to_remove_spend <- to_remove_tenure_spend_helper %>% filter(flag_spend) %>%  select(-starts_with("flag"))
log_check_result(
  condition = nrow(to_remove_spend) == 0,
  type = "augment spend",
  check_type = "validity",
  count = nrow(to_remove_spend)
)
if(nrow(to_remove_spend) > 0) add_and_write_sheet(Diagnostic_WB, "Removed_Invalid_Spend", to_remove_spend)

# INVALID SETUP DATE
to_remove_miss_setup_dt <- USCS_Sample[USCS_Sample$setup_dt %in% c("", "0001-01-01") | is.na(USCS_Sample$setup_dt),]
log_check_result(
  condition = nrow(to_remove_miss_setup_dt) == 0,
  type = "setup dates",
  check_type = "validity",
  count = nrow(to_remove_miss_setup_dt)
)

if(nrow(to_remove_miss_setup_dt) > 0) {
  to_remove_miss_setup_dt %>% 
    select(gmpi_base_cust_id, marketer_code, cell_code, raw_age, setup_dt, card_anniv_dt) %>%
    add_and_write_sheet(Diagnostic_WB, "Removed_Missing_Setup", .)
}

# MISSING MARKETER CODE
to_remove_miss_sp_code <- USCS_Sample[USCS_Sample$marketer_code == "" | is.na(USCS_Sample$marketer_code),]
log_check_result(
  condition = nrow(to_remove_miss_sp_code) == 0,
  type = "marketer codes",
  check_type = "missing",
  count = nrow(to_remove_miss_sp_code)
)

if(nrow(to_remove_miss_sp_code) > 0) add_and_write_sheet(Diagnostic_WB, "Removed_Missing_Marketer_Code", to_remove_miss_sp_code)

# LEADING SPACE IN ID
to_remove_blank_id <- USCS_Sample %>% filter(substring(gmpi_base_cust_id, 1, 1) == " ") 
log_check_result(
  condition = nrow(to_remove_blank_id) == 0,
  type = "customer IDs with leading spaces",
  check_type = "validity",
  count = nrow(to_remove_blank_id)
)

if(nrow(to_remove_blank_id) > 0) add_and_write_sheet(Diagnostic_WB, "Removed_Blank_ID", to_remove_blank_id)

# YOB
to_remove_yob <- USCS_Sample[is.na(USCS_Sample$raw_age) | between(USCS_Sample$raw_age, 120, 2000), ]
log_check_result(
  condition = nrow(to_remove_yob) == 0,
  type = "ages",
  check_type = "validity",
  count = nrow(to_remove_yob)
)

if(nrow(to_remove_yob) > 0) {
  to_remove_yob %>% 
    select(gmpi_base_cust_id, marketer_code, cell_code, raw_age, setup_dt, card_anniv_dt) %>%
    add_and_write_sheet(Diagnostic_WB, "Removed_YOB", .)
}
```


## Marketer Code Spend Checking
  - Is there anyone with spend <= 0 that shouldn’t be?
  - Are there products that can have spend <= 0 that have no observations with spend <= 0?

```{r Negative Spend Check}
# Perform the check (allowed negative spend marketer codes defined in config file)
negative_spend_validation_results <- USCS_Sample %>% filter(is_main) %>% check_negative_marketer_codes()
```

-- This is an example note from June 2023 of when Marketer Code 154 with allowed negative spend did not have any

```{r UC File Message}
# sp154 <- USCS_Sample %>% filter(is_main) %>% filter(marketer_code == 'SP154')
# 
#cli_alert_info('There were {nrow(sp154)} samples pulled for Marketer Code 154. The UC file for Q2 2023 shows that the post suppression count percentage is 0.1% for 0 spend. Given the small sample pulled for SP154 and the 0.1% likelihood that the sample is 0 spend, having no 0 spend in our sample is okay.')
# 
# sp154 %>% select(account_spend) %>% summary()
```

## New Open Segment

-   New Open Segment file received every May/June
-   The code reads in a list customer_ids classified segments.
-   There should be less than 3000 people overlapping with the sample and the open segment

```{r Load Open Seg message=FALSE}
# Load in new segment data
open_seg <- load_open_seg()
```

```{r Open Seg Checks}
open_seg_dupes <- open_seg[duplicated(open_seg$customer_id),]

log_section_start("Open Segment Duplicate ID Check")
log_check_result(
  condition = nrow(open_seg_dupes) == 0,
  type = "open segment customer IDs",
  check_type = "dupes",
  data = open_seg_dupes$customer_id
)

# Check overlap between the open segment and the sample
open_segment_checks <- check_open_seg_overlap(USCS_Sample, open_seg)

open_seg_freq <- open_seg %>% freq_table("OPEN_MANAGED_SEGMENT", caption="Open Managed Segment Freqs")
```

```{r Append Open Seg}
# Add the open segment info to the augment file
USCS_Sample <- USCS_Sample %>% left_join_suppress(mutate(open_seg, is_main = F))
```


## Performing Removals

```{r Store Pre Removals}
# We save a copy of the dataset and helper files here before the removals, so it's easy to not remove something if asked.
save(USCS_Sample, 
     to_remove_miss_spend, to_remove_miss_tenure, to_remove_miss_setup_dt, to_remove_tenure, to_remove_spend, to_remove_yob, 
     Diagnostic_WB, MONTH, YEAR,
     file="../Data/USCS_Sample_Preremovals-{Sys.Date()}.Rdata")

# Uncomment this to load in the image of the USCS_Sample dataframe before removals
# REMOVAL_DATE <- "2024-12-03
# load(f_str("../Data/USCS_Sample_Preremovals-{REMOVAL_DATE}.Rdata"))
```

**IF OPS SAY YOU SHOULD NOT REMOVE CERTAIN PEOPLE**
  - Comment out certain lines in the next chunk to not remove them

```{r Perform Removals}
USCS_Sample <- USCS_Sample %>% 
  remove_bad_sample(to_remove_miss_spend, "Missing Spend") %>% 
  remove_bad_sample(to_remove_miss_tenure, "Missing Tenure") %>% 
  remove_bad_sample(to_remove_miss_setup_dt, "Invalid Setup Date") %>% 
  remove_bad_sample(to_remove_tenure, "Invalid Tenure") %>% 
  remove_bad_sample(to_remove_spend, "Invalid Spend") %>% 
  remove_bad_sample(to_remove_yob, "Invalid YOB") 
```

## Save Workbook and Clear Workspace
```{r Save Workbook}
# Save the Diagnostic Workbook
saveWorkbook(Diagnostic_WB, file = f_str("../Files_to_send/USCS_Diagnostics_{MONTH}_{YEAR}-{Sys.Date()}.xlsx"), overwrite = TRUE)
```

```{r Clean up Workspace message=FALSE}
# Clean up the environment
rm.all.but(keep = c('USCS_Sample'))
source('USCS_Helper_Functions.R')
```

## Assign weighting conditions

- This chunk takes in the information from the target weight summary and extracts the conditions for the weighting segments
  
```{r Assign Weight Conditions}
# Load in weighting conditions
raw_weight_conditions <- load_weighting_conditions()

weight_conditions <- assign_weight_conditions(raw_weight_conditions)

#  Apply the weighting conditions and generate the segments
USCS_Weighted <- USCS_Sample %>% 
  mutate(weighting_segment = case_when(!!!rlang::parse_exprs(weight_conditions$full_cond)))
```

```{r Verify Weight Splits}
# Summary Stats by weighted segment
weight_summary <- create_weight_summary(USCS_Weighted) %>% make_nice_table("Weighting Segments Summary Table")

# Cross-tabulation of cell_code, weighting_segment, and spcode
weights_ncc_sp_code <- USCS_Weighted %>%
  freq_table(c('cell_code', 'weighting_segment', 'sp_code'), "Cross-tab of cell_code, weighting_segment, and sp_code")

# MAKE SURE ALL OBSERVATIONS HAVE A WEIGHTING SEGMENT | IF NOT, IDENTIFY WHAT HAPPENED IN JIM'S WEIGHTING FILE
unweighted <- weight_summary %>% filter(is.na(weighting_segment))

log_section_start("Weights")
log_check_result(
  condition = nrow(unweighted) == 0,
  type = "Weights",
  check_type = "missing",
  data = unweighted$weighting_segment
)
```

## Create New Variables

```{r New Variables}
USCS_New_Vars <- USCS_Weighted %>%
  mutate(
    # Setting Constants
    survey_type = "USCS",
    country = "United States",
    country_code = 90,
    language = "EN",
    
    sv_augment_cell = if_else(is_main, "NULL", str_extract(cell_code, "[0-9]{2}")), # NULL is default
    cv_augment_sample = ifelse(!is_main, 1, 2),
    
    sv_spend = case_when(
      is.na(account_spend) ~ 1L, # Since we set to missing spend to 0 later
      account_spend <=    0 ~ 1L,
      account_spend <  1500 ~ 2L,
      account_spend <  2500 ~ 3L,
      account_spend <  5000 ~ 4L,
      account_spend <  7500 ~ 5L,
      account_spend < 10000 ~ 6L,
      account_spend < 20000 ~ 7L,
      account_spend < 35000 ~ 8L,
      account_spend < 50000 ~ 9L,
      TRUE ~ 10L
    ),
    account_spend = coalesce(account_spend, 0), # Set missing spend to 0
    bf_fico_range = ifelse(fico_range == "", "", parse_number(fico_range)),
    account_share_of_wallet = ifelse(size_of_wallet != 0, account_spend / size_of_wallet, NA),  
    
    best_dma = ifelse(best_dma_cd %in% c(0, 999) | is.na(best_dma_cd), 
                  "REF",
                   as.character(best_dma_cd)),
    
    cv_interview_date = paste0(YEAR, MONTH_2_DIGITS),
    wv_weighting_segment = paste0(weighting_segment, cv_interview_date),
    
    bf_st_exp_enroll_in = case_when(
      st_exp_enroll_in == "" ~ "",
      TRUE ~ recode(st_exp_enroll_in, !!!ENROLLMENT_CODE_MAPPING, .default = "REF") # Defined in config
    ),
    
    bf_expo_enroll_in = case_when(
      expo_enroll_in == "" ~ "",
      TRUE ~ recode(expo_enroll_in, !!!ENROLLMENT_CODE_MAPPING, .default = "REF") # Defined in config
    ),
    
    # Defined in config
    bf_myca_flg = case_when(
      myca_flag == "" ~ "",
      TRUE ~ recode(myca_flag, !!!MYCA_MAPPING, .default = "R") # SAS cutoff "REF" to "R", so we have to keep it here
    ),
    
    bf_mr_in = case_when(
      mr_in == "" ~ "",
      TRUE ~ recode(mr_in, !!!MR_IN_MAPPING, .default = "REF") # Defined in config
    ),
    
    bf_purch_apr_rt = case_when(
      purch_apr_rt > 0 ~ round(purch_apr_rt,2) %>% as.character(),
      purch_apr_rt == -1 ~ "",
      .default = "REF"),
    
    cv_cs_et_type = case_when(
      between(tenure_var, 2, 4) ~ 1L,
      between(tenure_var, 5, 15) ~ 2L,
      .default = 3L
    ),
    
    # Defined in config
    cv_portfolio = unname(PORTFOLIO_MAPPING[marketer_code]),
    
    cv_mr_category = recode(mr_tier_prog_cd, !!!MR_CATEGORY_MAPPING, .default = NA_integer_), # Defined in config
    
    card_name = recode(marketer_code, !!!CARD_NAME_MAPPING), # Defined in config
    
    cv_amex_has_fee = if_else(
      marketer_code %in% names(AMEX_FEE_MAPPING),
      unname(AMEX_FEE_MAPPING[marketer_code]), # Defined in config
      "REF"
    ),
  
    #card anniversary date
    card_anniv_dt = na_if(card_anniv_dt, "0001-01-01"),
    anniv = as_date(card_anniv_dt, format = "%Y-%m-%d"),
    bf_card_anniv_year = year(anniv),
    bf_card_anniv_month = month(anniv),
    
    # Setup date
    bf_setup_day = day(setup),
    bf_setup_month = month(setup),
    bf_setup_year = year(setup),
       
    # Prog Enter Date
    mr_init_enroll_dt = na_if(mr_init_enroll_dt, "0001-01-01"),
    enrolls = as_date(mr_init_enroll_dt, format = "%Y-%m-%d"),
    bf_mr_init_enroll_year = year(enrolls),
    bf_mr_init_enroll_month = month(enrolls),
    bf_mr_init_enroll_day = day(enrolls),
       
    #Age
    dInterviewDate = YEAR + (MONTH_NO/12),
    dYOB = floor(dInterviewDate - raw_age),
    year_of_birth = ifelse(is.na(raw_age) | dYOB < 1850 | dYOB > (year(Sys.Date()) - 17), 
                           "", 
                           as.character(dYOB)),
  
    generation = case_when(
      year_of_birth == "" ~ "",
      TRUE ~ GENERATION_MAPPING$labels[findInterval(dYOB, GENERATION_MAPPING$thresholds)] # Defined in config
    ), 
  
    bdl_fico_bucket = case_when(is.na(raw_fico) | raw_fico == -1 ~ "",
                                raw_fico < 650 ~ "1",
                                raw_fico < 720 ~ "2",
                                raw_fico >= 720 ~ "3"),
    
    CCSG_CENTURION_TIER = ""  # Set to an empty variable. Use to come from a file that has not been updated in a long time
    )
```

## CHECKS FOR NEW VARIABLES

- Most of these need to be hand checked since they were created by the same formulas that would be used to check their correctness

```{r New Variable Checks}
log_section_start("New Variable Checks")

# Early Tenure
missing_cs_et <- USCS_New_Vars %>% filter(is.na(cv_cs_et_type)) 
log_check_result(nrow(missing_cs_et) == 0, "Early Tenure Type", "missing", nrow(missing_cs_et))

# DMA
invalid_dma_cd <- USCS_New_Vars %>% filter(replace_na(best_dma_cd,"") %in% c('','999','0'))
invalid_dma <- USCS_New_Vars %>% filter(replace_na(best_dma,"") %in% c('','999','0'))
log_check_result(nrow(invalid_dma_cd) == 0, "DMA CD", "validity")
log_check_result(nrow(invalid_dma) == 0, "DMA", "validity")

# Spend
missing_spend <- USCS_New_Vars %>% filter(is.na(account_spend))
log_check_result(nrow(missing_spend) == 0, "Account Spend", "missing", count = nrow(missing_spend))

# ENroll
ref_enroll <- USCS_New_Vars %>% filter(bf_st_exp_enroll_in == "REF")
log_check_result(nrow(ref_enroll) == 0, "ST Exp Enroll", "missing", count = nrow(ref_enroll))

# MYCA
ref_myca_flag <- USCS_New_Vars %>% filter(myca_flag == "REF")
log_check_result(nrow(ref_myca_flag) == 0, "MYCA Flag", "missing", count = nrow(ref_myca_flag))

# MR IN
missing_mr_in <- USCS_New_Vars %>% filter(is.na(bf_mr_in) | bf_mr_in == "")
log_check_result(nrow(missing_mr_in) == 0, "MR IN", "missing", count = nrow(missing_mr_in))

# Fee
missing_fee <- USCS_New_Vars %>% filter(is.na(cv_amex_has_fee))
log_check_result(nrow(missing_fee) == 0, "Has Fee Marketer Code", "missing", missing_fee$marketer_code)

# Portfolio
missing_portfolio <- USCS_New_Vars %>% filter(is.na(cv_portfolio))
log_check_result(nrow(missing_portfolio) == 0, "Portfolio Marketer Code", "missing", missing_portfolio$marketer_code)

# Manual Checks
yobs_check <- USCS_New_Vars %>% mutate(age = ceiling(raw_age)) %>% 
  distinct(dInterviewDate, dYOB, age, year_of_birth) %>% arrange(age) %>% 
  make_nice_table("Checking year of birth calculations") # Are ages correct

gen_check <- USCS_New_Vars %>% distinct(year_of_birth, generation) %>% 
  arrange(year_of_birth) %>% 
  make_nice_table("Checking Generation calculations")

fico_check <- USCS_New_Vars %>% distinct(raw_fico, bdl_fico_bucket) %>% 
  arrange(bdl_fico_bucket, raw_fico) %>% 
  make_nice_table("Checking FICO Bucket")
```


```{r Missing Names}
# Identify people with missing first and last names
missing_name <- USCS_New_Vars %>% filter(is.na(first_nm) | is.na(last_nm)) %>% 
  select(customer_id,first_nm, last_nm)

log_check_result(nrow(missing_name) == 0, "First or Last Name", "missing", count=nrow(missing_name))

# Fill in the blank names with "Valued Card Member" because First and Last name
USCS_New_Vars <- USCS_New_Vars %>% 
  mutate(needs_default_name = is.na(first_nm) | is.na(last_nm) | nchar(first_nm) == 10,
    first_nm = if_else(needs_default_name, "Valued Card", first_nm),
         last_nm = if_else(needs_default_name, "Member", last_nm)) %>% select(-needs_default_name)
```

```{r Subject Line Insert message=F}
# Read in Subject Line Code Info
subject_line_insert_info <- load_subject_line_info()

# check if there are records that did not match with the Subject line insert file
USCS_New_Vars <- USCS_New_Vars %>% left_join_suppress(subject_line_insert_info)

miss_inserts <- USCS_New_Vars[is.na(USCS_New_Vars$subject_line_insert),]
log_check_result(nrow(miss_inserts) == 0, "Subject Line Insert", "missing", count = nrow(miss_inserts))

ia_subline_freq <- USCS_New_Vars %>% 
  freq_table(c("ia_id", "subject_line_insert"), 
             "Freq table IA ID vs Subject Line insert")
```

```{r Name Replacement message = F}
# Create new variable and replace empty values with "American Express Card"
USCS_New_Vars <- USCS_New_Vars %>% 
  mutate(sv_subject_line_insert = if_else(subject_line_insert == "", "American Express Card", subject_line_insert))

# Read in Card Art URLs
card_art_info <- load_card_art()

# Merge data
USCS_New_Vars <- USCS_New_Vars %>% left_join_suppress(card_art_info)

marketer_sv_card_freq <- USCS_New_Vars %>% freq_table(c("marketer_code","sv_card_art"), "Marketer Code vs SV Card Freq Table")
```

```{r Reformatting}
date_cols <- c("setup_dt", "card_anniv_dt", "mr_init_enroll_dt") # date columns to "M/D/YYYY" format

rounding_cols <- c("account_spend", "size_of_wallet", "share_of_wallet_amex", 
                  "customer_spend", "raw_age", "t_add")

ref_cols <- c("card_anniv_dt", "bf_card_anniv_year", "bf_card_anniv_month",
              "setup_dt", "bf_setup_year", "bf_setup_month", "bf_setup_day")

USCS_Reformatted <- USCS_New_Vars %>% 
  mutate(
    # Format dates ; Remove leading 0s
    across(all_of(date_cols),  ~gsub("^0", "", gsub("/0", "/", format(as.Date(.x), "%m/%d/%Y")))),
    
    # Truncate ID
    gmpi_base_cust_id = substr(gmpi_base_cust_id, 5, 19),
    
    # Round columns
    across(all_of(rounding_cols), ~round(., 2)),
    account_share_of_wallet = txt_sprintf("%.14f", account_share_of_wallet),
    
    # Handle missing values
    across(all_of(ref_cols), ~ifelse(. == "" | is.na(.), "REF", .))
  )
```

```{r Final Selection message=F}
# Merging the data frames
USCS_Final <- USCS_Reformatted %>% 
  arrange(is_main, parse_number(cell_code), sp_code, sv_spend, t_add) %>% # Sort Data 
  set_names(str_to_upper(names(.))) %>% 
  # Choose only desired variables and name them how we want them named
  select(BF_GMPI_BASE_CUST_ID = GMPI_BASE_CUST_ID,
        FIRST_NM,
        LAST_NM,
        BF_CITY_NM = CITY_NM,
        BF_STATE_TX = STATE_TX,
        BF_US_ZIP = US_ZIP,
        BF_LAST5 = LAST5,
        BF_IA_ID = IA_ID,
        BF_FMLY_DS_TX = FMLY_DS_TX,
        BF_CARD_ROLLUP_DS_TX = CARD_ROLLUP_DS_TX,
        BF_CONS_FRIENDLY_DS_TX = CONS_FRIENDLY_DS_TX,
        BF_SETUP_DT = SETUP_DT,
        BF_BEST_DMA_CD = BEST_DMA,
        BF_MAIL_ID = MAIL_ID,
        BF_CELL_CODE = CELL_CODE,
        BF_MARKETER_CODE = MARKETER_CODE,
        BF_MYCA_FLG,
        BF_MR_IN,
        BF_ACCOUNT_SPEND = ACCOUNT_SPEND,
        BF_SIZE_OF_WALLET = SIZE_OF_WALLET,
        BF_SHARE_OF_WALLET_AMEX = SHARE_OF_WALLET_AMEX,
        BF_CARD_ANNIV_DT = CARD_ANNIV_DT,
        BF_AGE_RANGE = AGE_RANGE,
        BF_CUSTOMER_SPEND = CUSTOMER_SPEND,
        BF_FICO_RANGE,
        BF_ACTIVE_SUPP_CT = ACTIVE_SUPP_CT,
        BF_ST_EXP_ENROLL_IN,
        BF_EXPO_ENROLL_IN,
        BF_MR_TIER_PROG_CD = MR_TIER_PROG_CD,
        BF_MR_INIT_ENROLL_DT = MR_INIT_ENROLL_DT,
        BF_AVLBL_PNTS = AVLBL_PNTS,
        BF_ACCT_TRANS_PNTS_NO = ACCT_TRANS_PNTS_NO,
        BF_TOT_RVLV_INT_AM = TOT_RVLV_INT_AM,
        BF_RVLV_MTHS_NO = RVLV_MTHS_NO,
        BF_TOT_LOC_INT_AM = TOT_LOC_INT_AM,
        BF_TOT_LOC_INT_MTH_NO = TOT_LOC_INT_MTH_NO,
        BF_TOT_LOC_AM = TOT_LOC_AM,
        SV_SP_CODE = SP_CODE,
        SV_AUGMENT_CELL,
        SV_STUDY_OPENEND = MV_NPS_IND,
        SV_MR_IN = MR_IN_N,
        SV_TENURE_QUANT = TENURE_VAR,
        BF_RDM_NET_12M_CT = RDM_NET_12M_CT,
        BF_LINE_OF_CREDIT_AM = LINE_OF_CREDIT_AM,
        BF_PURCH_APR_RT,
        SV_SUBJECT_LINE = SUBJECT_LINE,
        SV_PRODUCT_TENURE = T_ADD,
        WV_WEIGHTING_SEGMENT,
        SV_SPEND,
        SURVEY_TYPE,
        COUNTRY,
        COUNTRY_CODE,
        LANGUAGE,
        CV_PORTFOLIO,
        CV_INTERVIEW_DATE,
        CV_AMEX_HAS_FEE,
        CV_MR_CATEGORY,
        CV_CS_ET_TYPE,
        CCSG_CENTURION_TIER,
        CV_BF_ACCOUNT_SHARE_OF_WALLET = ACCOUNT_SHARE_OF_WALLET,
        BF_CARD_ANNIV_YEAR,
        BF_CARD_ANNIV_MONTH,
        BF_MR_INIT_ENROLL_YEAR,
        BF_MR_INIT_ENROLL_MONTH,
        BF_MR_INIT_ENROLL_DAY,
        BF_SETUP_YEAR,
        BF_SETUP_MONTH,
        BF_SETUP_DAY,
        CARD_NAME,
        BDL_AGE = RAW_AGE,
        BDL_FICO_SCORE = RAW_FICO,
        YEAR_OF_BIRTH,
        CV_Generation_New = GENERATION,
        BDL_FICO_BUCKET,
        SV_SUBJECT_LINE_INSERT,
        SV_CARD_ART)
```


```{r Write to CSV}
USCS_Final %>% write_csv("../Files_to_send/AmexGABMUSCSSurvey_{YEAR}{MONTH_2_DIGITS}_{Sys.Date()}.csv" %>% f_str(), na ="")
```

```{r Save}
# Store final dataset for ease of loading in formats
# save(USCS_Final, file=f_str("../Data/USCS_Final_{MONTH}_{YEAR}-{Sys.Date()}.Rdata"))
```

```{r Clean up Workspace}
rm.all.but(keep=c('USCS_Final', 'MONTH', 'YEAR'))
```

```{r Reload in Final Dataset}
# Load final dataset for quick checks if needed
# FINAL_SAVE_DATE <- "2024-12-03"
# load(f_str("../Data/USCS_Final_{MONTH}_{YEAR}-{FINAL_SAVE_DATE}.Rdata"))
```

