---
title: "USCS Prep Sample for Qualtrics 1"
output:
  html_document:
    df_print: paged
editor_options:
  markdown:
    wrap: 75
---

### Preparatory Steps

Consult `ReadMe.md` for instructions on how to configure the inputs
properly before running this script


Remember to update file paths and variables in `Config_and_Helper.R`

### Notes

-   As a heads up we tripled the recommended amount for SP 133.

-   Please note the variable `TOT_RVLV_INT_AM` was removed from the sample
    file but the spaces for it remain. **The new Customer Acquisition Code
    variable may show up on the end of this file. If you see it, please
    remove it.**

-   If you have any questions about the files or checks to be done, please
    let me or the PM team know. The subject lines will now be the same for
    everyone as everyone is NPS to start.

-   All NPS respondents, including NPS augments, will see subject line "6"
    (10 Quick Questions about your [American Express Card])."

-   **This code will output warnings and messages.** The warnings indicate
    a check is not met. These will be printouts with "Warning:" before
    them. If a check is passed, a message will be printed with "SUCCESS:"
    before it. If any warnings are printed, figure out why and report if
    the warning says to.

### Dependencies

```{r Load in Packages, message=FALSE, warning=FALSE}
if (!require("pacman")) install.packages("pacman")

# Loads in necessary packages, and installs them if you don't have them installed
pacman::p_load("tidyverse",
               "readxl",
               "stringi",
               "varhandle")

# Load in configuration file variables and functions
source('Config_and_Helpers.R') 

options(scipen = 99999, # Remove scientific notation
        dplyr.summarise.inform = FALSE) # Remove summarize messages

knitr::opts_chunk$set(results = "asis", # Prints html tables nicely
                      echo=TRUE) # Show all code chunks in the output
```

### Data Loading

```{r Load in base and spend dataframes}
all_base <- load_base() 
all_spend <- load_spend()

f_str("There were {format(nrow(all_base), big.mark = ',')} observations loaded in for BASE") %>% message()
f_str("There were {format(nrow(all_spend),big.mark = ',')} observations loaded in for SPEND") %>% message()
```

```{r Missing Value Summary}
# Variables to summarize number of missing values
miss_vars <- c("first_nm", 
               'last_nm',
               "raw_fico",
               "fico_range",
               "raw_age",
               "share_of_wallet_amex",
               "size_of_wallet",
               "customer_spend",
               "account_spend")

# Number and Percent of missing values for key variables
miss_vals <- all_base %>%
  select(all_of(miss_vars)) %>%
  summarise_all(~sum(is.na(.))) %>%
  pivot_longer(cols = everything(), names_to = "Variable", values_to = "n_missing") %>%
  mutate("Percent Missing" = paste0(round(n_missing / nrow(all_base) * 100, 4), " %")) %>% 
  arrange(desc(n_missing)) %>% make_nice_table("Number of Missing Values per Key Variable")
```


```{r Filtering base and spend}
# Change these monthly based on OPS instructions
# Comment out filters that do not need to be applied

all_base <- all_base %>% 
  # *Change new_smart_rev to numeric
  #mutate(new_smart_rev = as.numeric(new_smart_rev_char)) %>%
  
  #*From Ops email: (please take out all counts for Augment 54);
  # filter(!cell_code %in% c("","CNGR54")) %>% 
  #*from ops email 9 28 22: #take out the three people missing marketer_code
  filter(marketer_code != "") 

all_spend <- all_spend %>%
  rename(gmpi_base_cust_id = customer_id) %>% 
  # Remove records with blank space at start of ID
  filter(substring(gmpi_base_cust_id, 1, 1) != " ") 
```


### Cell Code Checking

-   Compare the total amount of main sample received to the amount of
    sample requested
-   Verify no missing cell codes

```{r Check Cell Codes, message=FALSE}
# Create a frequency table of each cell code
cell_code_freq <- all_base %>% 
  freq_table("cell_code", caption = "Cell Code Frequencies")
```

```{r }
# Break the cell codes into the main survey codes and augmented survey codes
# Main Survey has 'Cell_Codes' that start with 'CCSG' 
main_survey_ccs <- cell_code_freq %>% filter(str_starts(cell_code, "CCSG")) 
aug_survey_ccs <- cell_code_freq %>% 
  filter(!str_starts(cell_code, "CCSG") & str_starts(cell_code, "C"))
```

```{r message=FALSE}
# Load in the expected frequencies from the helper file
req_sp_codes <- read_excel(SAMPLE_PREP_PATH,
                           sheet = "Sp_Code_Freqs") %>% 
  set_names(c("sp_code", "card_name", "Total")) %>% 
  mutate(sp_code = glue("SP{sp_code}")) %>% 
  drop_na(sp_code)
```

```{r}
if (sum(main_survey_ccs$Freq) != sum(req_sp_codes$Total)){
  warning("The Main sample recieved does not match the sample requested
          Provide an explanation or resolution to the difference. Figure out what's wrong. 
          Details may become more apparent in step 10 below")
} else{
  message("SUCCESS: The size of the main Sample recieved matches the sample requested")
}

missing_ccs <- cell_code_freq %>% dplyr::select(cell_code) %>% 
  filter(!cell_code %in% unique(c(main_survey_ccs$cell_code,
                                  aug_survey_ccs$cell_code)))

if (nrow(missing_ccs) > 0) {
  warning("Cell Code detected not in main or augmented survey detected. Check MISSING_CCS dataframe for these codes")
} else{
  message("SUCCESS: All cell codes match format for main or augmented surveys")
}
```

### Check to make sure everyone has a spend and tenure and new-product-tenure.

-   cell_code 68 can have any marketer code but if it does have 135, notify
    PM

```{r}
# Check missing account spend and tenure add
acct_spend_add_t_NAs <- all_base %>% dplyr::select(account_spend, t_add) %>% 
  sapply(function(x) sum(is.na(x))) %>% as.data.frame() %>% 
  set_names("No. Missing Values")

acct_spend_add_t_NAs_tab <- acct_spend_add_t_NAs %>% 
  make_nice_table("Missing Values Account Spend and Tenure Add") 

if(acct_spend_add_t_NAs["account_spend",] > 0){
  warning("ACCOUNT SPEND has missing values")
} else{
  message("SUCCESS: ACCOUNT SPEND does not have missing values")
}

if(acct_spend_add_t_NAs["t_add",] > 0){
  warning("New Product Tenure has missing values")
}else{
  message("SUCCESS: New Product Tenure does not have missing values")
}
# Check missing set up dates
miss_setup_dt <- all_base[all_base$setup_dt == "",]
if (nrow(miss_setup_dt) > 0){
  warning("Missing Set up Date. Check miss_setup_dt variable")
}else{
  message("SUCCESS: No missing set up dates")
}

# Check missing marketer codes
miss_marketer_code <- all_base[all_base$marketer_code == "",]
if (nrow(miss_marketer_code) > 0){
  warning("Missing Marketer Code. Check miss_marketer_code variable")
}else{
  message("SUCCESS: No missing marketer codes")
}

cn68_market_codes <- all_base[all_base$cell_code == 'CN68',] %>% 
  dplyr::select(cell_code, marketer_code) %>% 
  mutate(is_not_sp135 = marketer_code != "SP135")

if (nrow(cn68_market_codes) > 0){
  warning("There are observations with Cell Code 'CN68'")
  if (sum(cn68_market_codes$is_not_sp135) > 0){
  warning("Not all marketer codes are SP135 for cell codes CN68. Alert OPS/PM") 
  } else {
    message("ITS OKAY because all marketer codes are SP135")
  }
} else{
    message("SUCCESS: No observations with Cell Code 'CN68'")
  }
```

**ACTION NEEDED**

-   The next two chunks output two csv's to be sent to the operations
    manager in an email

    -   CSV `Main_Code_Freqs_MONTH_YEAR.csv` is found in the
        `Files_to_send` folder

    -   CSV `Cell_Code_Freqs_MONTH_YEAR.csv` is found in the
        `Files_to_send` folder

```{r }
# Table with marketer code frequencies for cell codes "CCSG01", "CCSG02", "CCSG03"
main_code_freq <- all_base %>% 
  filter(cell_code %in% c("CCSG01", "CCSG02", "CCSG03")) %>% 
  freq_table("marketer_code", 
             caption = "Marketer Code Frequencies for Main Cell Codes")

# Write to csv to send to OPS Manager 
main_code_freq %>%  
  write_csv(f_str("../Files_to_send/Main_Code_Freqs_{MONTH}_{YEAR}.csv")) 
```

```{r}
cell_code_freq <- cell_code_freq %>% 
  # Extract two digit number from cell code and append it to either Drop or Augment
  mutate(naw_cell_code = if_else(str_starts(cell_code, "CCS"),
                                 paste("CCSG DROP", 
                                        str_extract(cell_code, "[0-9]{2}")),
                                 paste("Augment Cell",
                                       str_extract(cell_code, "[0-9]{2}")))
         ) %>% 
  dplyr::select(cell_code, naw_cell_code, Freq) %>% 
  arrange(str_extract(cell_code, "[0-9]{2}"))

# Save file to be sent to PM
cell_code_freq %>% 
  write_csv(f_str("../Files_to_send/Cell_Code_Freqs_{MONTH}_{YEAR}.csv"))

ccf <- cell_code_freq %>% 
  make_nice_table("Cell Code Frequencies with NAW Cell Codes")
```

### Check validity of userID and password

```{r}
invalid <- all_base %>% 
  dplyr::select(account_number, personalization1, personalization2) %>% 
  mutate(new_user_id = gsub("  ", "", personalization1) %>% trimws(), # Remove double spaces and surrounding white space from username
         new_password = gsub("  ", "", personalization2) %>% trimws(),  # Remove double spaces and surrounding white space from password
         VALID = case_when(
           # Missing Value
           new_user_id == "" | new_password == "" ~ 1, 
           # Wrong Length
           nchar(new_user_id) != 7 | nchar(new_password) != 8 ~ 2,
           # First character of ID not 'u'
           substr(new_user_id, 1, 1) != 'u' ~ 3, 
           # userID should be all digits and password should be characters
           !(substr(new_user_id, 2, 7) %>% is_numbers_only() & 
               new_password %>% is_letters_only) ~ 4, 
           TRUE ~ 0) # If none of the above cases, it's valid
         ) %>% 
  filter(VALID != 0) # Remove all valid cases

if (nrow(invalid) > 0){
  warning("Some invalid passwords or usernames found. Report to Manager")
  invalid %>% make_nice_table("Invalid Usernames and Passwords")
} else{
  message("SUCCESS: All passwords and usernames valid")
}
```

### Check for duplicates

```{r}
all_base_dupes <- all_base[duplicated(all_base$gmpi_base_cust_id),]
all_spend_dupes <- all_spend[duplicated(all_spend$gmpi_base_cust_id),]

if (nrow(all_base_dupes) > 0){
  warning("Duplicate Base customer IDs in the Allbase dataframe")
  print(all_base_dupes$gmpi_base_cust_id)
} else{
  message("SUCCESS: No duplicates in Allbase dataframe")}

if (nrow(all_spend_dupes) > 0){
  warning("Duplicate base customer IDs in the Allspend dataframe")
  print(all_spend_dupes$gmpi_base_cust_id)
} else{
  message("SUCCESS: No duplicates in Allspend dataframe")}
```

### Merge Allspend and Allbase

-   Code to account for the all Augments when assigning values to
    'naw_cell_code'
-   Add code for new Augments
-   Make sure the proper number of records remain

```{r}
all <- inner_join(all_base, all_spend, by = "gmpi_base_cust_id") %>% 
  mutate(setup_year = substr(setup_dt, 1, 4) %>% as.numeric(),
         setup_month = substr(setup_dt, 6,7) %>% as.numeric(),
         tenure_var = 12*(YEAR-1-setup_year)+(MONTH_NO+12-setup_month),
         account_spend = as.numeric(account_spend),
         tenure_cat = case_when(
           tenure_var <   5 ~ 1,
           tenure_var <  16 ~ 2,
           tenure_var <  25 ~ 3,
           tenure_var <  49 ~ 4,
           tenure_var <  73 ~ 5,
           tenure_var < 109 ~ 6,
           tenure_var < 145 ~ 7,
           tenure_var < 181 ~ 8,
           tenure_var < 241 ~ 9,
           TRUE ~ 10),
         
         spend = case_when(
           account_spend <=    0 ~ "A",
           account_spend <  1500 ~ "B",
           account_spend <  2500 ~ "C",
           account_spend <  5000 ~ "D",
           account_spend <  7500 ~ "E",
           account_spend < 10000 ~ "F",
           account_spend < 20000 ~ "G",
           account_spend < 35000 ~ "H",
           account_spend < 50000 ~ "I",
           TRUE ~ "J"),
         
         top_spender = if_else(account_spend < 50000, 0, 1),
         # Spend cat3 is the numeric value of the account spend's alphabet positions (A:1, B:2 ... J:10)
         spend_cat3 = match(spend, LETTERS), 
         
         naw_cell_code = if_else(str_starts(cell_code, "CCSG"),
                                 gsub("CCSG", "DROP", cell_code),
                                 gsub("[A-Z]{2,}", "CELL", cell_code)),
         
         naw_type = if_else(cell_code %in% c("CCSG01", "CCSG02", "CCSG03"),
                            "MAIN",
                            "AUGMENT")
         )


if (nrow(all) != nrow(all_base)){
  warning("Size of merged dataframe does not match original dataframe.")
} else{
  message("SUCCESS: Size of merged dataframe matches original dataframe")
}

```

```{r}
# Save datasets and remove from memory
all_base %>% write_csv("../Data/all_base_{MONTH}_{YEAR}.csv" %>% f_str())
all_spend %>% write_csv("../Data/all_spend_{MONTH}_{YEAR}.csv" %>% f_str())
#rm(all_base, all_spend) 
```

### Checking for Duplicate Keys in Merged Data frame

```{r message=FALSE}
# First checking distribution of sample by Augment/MAIN;
naw_freq_table <- all %>%
  freq_table(c("naw_type", "naw_cell_code"),
             caption="Naw Type vs Naw Cell Code Frequencies")
```

```{r }
# Identify duplicates for customer id and username/password
cust_id_dupes <- all[duplicated(all$gmpi_base_cust_id),]
pers_dupes <- all[duplicated(all[,c("personalization1", "personalization2")]),]

if (nrow(cust_id_dupes) > 0){
  warning("There are customer ID duplicates in the merged dataframe")
  print(cust_id_dupes$gmpi_base_cust_id)
} else{
  message("SUCCESS: No Customer ID duplicates in the merged dataframe")
}

if (nrow(pers_dupes) > 0){
  warning("There are userID/password duplicates in the merged dataframe")
  print(pers_dupes[,c("personalization1", "personalization2")])
} else{
  message("SUCCESS: No userID/password duplicates in the merged dataframe")
}
```

### DMA Frequency

-   Make sure all DMA Codes are valid using the `DMA_Checks` sheet of the
    sample prep excel file.

```{r message=FALSE}
# Load in valid dmas
valid_dmas <- read_excel(SAMPLE_PREP_PATH,
                         sheet = "Valid_DMA_Codes") %>% 
  pull(Valid_DMA)
```

```{r }
# identify invalid dma's if any and get frequencies
invalid_dmas <- all %>% filter(!best_dma_cd %in% valid_dmas) %>% group_by(best_dma_cd) %>% summarize(n = n()) 

if (nrow(invalid_dmas) > 0){
  warning("There are invlaid DMA Codes in the file. Here are the codes and number of occurrences:")
  invalid_dmas %>% make_nice_table("Invalid DMA Code Frequencies") 
} else{
  message("SUCCESS: No invalid DMAs found in file")
}
```

### Frequency Tables for Spend and Tenure

-   Split the sample into Main and Augment

-   Frequency tables of spend tenure categories, and tenure_var for main
    samples

```{r}
# Split dataframe into main and augmented
main <- all %>% filter(naw_type == "MAIN") %>% 
  mutate(customer_id = gmpi_base_cust_id %>% as.numeric())
augment <- all %>% filter(naw_type == "AUGMENT")

```

```{r}
spend_freq_table <- main %>% 
  freq_table("spend", caption="Spend Category Frequencies")

tenure_freq_table <- main %>% 
  freq_table("tenure_cat", caption="Tenure Category Frequencies")

spend_freq_table_cat1 <- main %>% 
  filter(tenure_cat == 1) %>%
  freq_table("spend", caption="Spend Category Freqs for Tenure Category 1")

tenure_freq_table_cat1 <- main %>% 
  filter(tenure_cat == 1) %>% 
  freq_table("tenure_var", caption="Tenure Var Frequencies for Tenure Category 1")
```

### Sp Code Checking

-   Compare totals for desired sp codes to requested sp code totals

```{r}
main_sp_codes <- main %>% 
  freq_table("marketer_code", caption = "Sp Code Frequencies")
```

```{r}
# Check if the requested totals for each code matches the observed total
check_sp_codes <- main_sp_codes %>% 
  dplyr::select(marketer_code, Freq) %>% 
  left_join(req_sp_codes, by = c("marketer_code" = "sp_code")) %>% 
  mutate(difference = abs(Freq - Total)) %>% # This difference should be 0
  rename(Obs_Freq = Freq, Req_Freq = Total)


if (sum(check_sp_codes$difference) > 0){
  warning("Frequencies of Observed Sp Codes do not match requested totals for the following codes")
  print(check_sp_codes %>% filter(difference > 0))
} else{
  message("SUCCESS: All observed frequencies of sp codes match requested totals. ")
}
```

-   Ensure Requested Sp Codes do not have spending category A.
  - Is there anyone with spend <= 0 that shouldn’t be?
  - Are there products that can have spend <= 0 that have no observations with spend <= 0?


```{r}
# The sp codes below should not have SPEND <= 0;
sp_code_no_a <- c("SP111",
                  "SP112",
                  "SP113",
                  "SP114",
                  "SP115",
                  "SP117",
                  "SP118",
                  "SP123",
                  "SP127",
                  "SP132",
                  "SP136",
                  "SP145",
                  "SP153",
                  "SP156") # SP 156 added in JULY 2018

# Sp codes that are allowed to have no or negative spend
sp_code_a <- main$marketer_code[!main$marketer_code %in% sp_code_no_a] %>% unique()

# Sp codes observed to have spend <= 0
obs_sp_code_a <- main[main$spend == "A",]$marketer_code %>% unique()

# Identify if sp codes that should not have no spend have no spend
wrong_no_spends <- sp_code_no_a[sp_code_no_a %in% obs_sp_code_a]

# Identify if sp_codes that can have no spend have observation with no spend
missing_no_spends <- sp_code_a[!sp_code_a %in% obs_sp_code_a]

if (length(wrong_no_spends) > 0) {
  for (code in wrong_no_spends) {
    warning("Sp Code: {code} has spend <= 0 when it should not" %>% f_str())
    cat("\n")}
  warning("Alert Operations for confirmation to exclude them") # This is not in the code and would need to be added
} else{
  message("SUCCESS: All SP Codes who should not have spend <= 0, do not have spend <= 0")
} 


if (length(missing_no_spends) > 0) {
  for (code in missing_no_spends) {
    warning("Sp Code: {code} has no observations spend <= 0 when it is allowed too" %>% f_str())
    cat("\n")}
  warning("Check the UC file to see what proportion of the pre and post suppression counts are for $0 spend on that product.  Given the sample request, how likely is it that we received no $0 spenders? If it seems unreasonable, you should discuss the matter with operations")
} else{
  message("SUCCESS: All SP Codes who can have spend <= 0, have observations with spend <= 0")
} 
```


### New Open Segment

-   New Open Segment file received every May/June

-   The code reads in a list customer_ids classified segments.

-   No one in the Main sample should be in this file. The dataset that is
    created in the merge in the last step should have no records.

    -   If someone appears here, note and resolve/explain the issue

```{r message=FALSE}
# Load in new segment data
open_seg <- read_csv(OPEN_SEG_PATH) %>% 
  rename(gmpi_base_cust_id = cust_xref_id) %>% 
  mutate(customer_id = gmpi_base_cust_id %>% as.numeric()) # Get numeric ID
```

```{r}
# check distributions

# Customer ID Distribution in Main
cid_main <- main %>% 
  dplyr::select(customer_id_main = customer_id) %>% 
  summary() %>% make_nice_table("Customer ID Main Descriptive Stats")

# Open Segment Customer ID Distribution
cid_open <- open_seg %>%  
  dplyr::select(customer_id_open_seg = customer_id) %>% 
  summary() %>% make_nice_table("Customer ID Open Segment Descriptive Stats")

open_seg_freq <- open_seg %>% 
  freq_table("OPEN_MANAGED_SEGMENT", caption="Open Managed Segment Freqs")

open_seg_dupes <- open_seg[duplicated(open_seg$customer_id),]

if (nrow(open_seg_dupes) > 0){
  warning("Duplicated Customer IDs in New Open Segment File")
} else{
  message("SUCCESS: NO Duplicated Customer IDs in New Open Segment File")
}
```

```{r}
# Check if someone in the main file is in the open segment file
open_seg_check <- main %>% 
  inner_join(open_seg, by = c("gmpi_base_cust_id", "customer_id"))

if (nrow(open_seg_check) > 0){
  warning("Customers in the main file appear in the new segment file")
  cat('\n')
  if (nrow(open_seg_check) > 3000){
    warning("More than 3000 main file customers appear in the new segment. REPORT")
  } else{
   message("Less than 3000 main file customers appear in the new segment. Note and explain these customers. No need to report")
  }
} else{
  message("SUCCESS: No main file customers appear in the new segment")
}
```

```{r }
# Generate count for early and non-early tenure
et_tab <- main %>% 
  count(marketer_code, tenure_cat) %>%
  spread(tenure_cat, n, fill = 0)

et_tab <- et_tab %>% 
  # Create new variables for the split of early and non-early tenure counts
  mutate(et = `1`,
         non_et = rowSums(et_tab[3:11])) %>% 
  dplyr::select(marketer_code, et, non_et) %>% 
  janitor::adorn_totals('row') %>% 
  make_nice_table("Early vs Non-Early Tenure by SP Code")
```

### Diagnostic Tests

-   Keeping the 'Selected' functionality in for now.

```{r}
mrktr_naw <- table(main$marketer_code, main$naw_cell_code) %>%
  make_nice_table("Marketer Code vs NAw Cell Code")

main <- main %>% mutate(selected = 0,
                           # Extract marketer code (i.e. 101 from SP101)
                          sp_code = str_extract(marketer_code, "[0-9]{3}") %>% 
                            as.numeric(),
                           # Extract drop code (i.e. 1 from DROP 01)
                          drop_code = str_extract(naw_cell_code, "[0-9]{2}") %>% 
                            as.numeric(),
                          mv_nps_ind = if_else(selected == 0, "NPS", "MV"),
                          mr_in_n = if_else(mr_in == 'Y', 1, 2),
                          subject_line = if_else(selected == 0, 6, 7))
```

```{r }
write_csv(all, "../Data/all_{MONTH}_{YEAR}.csv" %>% f_str())
write_csv(main, "../Data/main_{MONTH}_{YEAR}.csv" %>% f_str())
```

```{r}
mr_in_ct <- table(main$mr_in,main$mr_in_n)

if (mr_in_ct[1,1] == 0 & mr_in_ct[2,2] == 0){
  message("SUCCESS: MR IN split worked correctly")
} else{
  warning("MR IN split did not work correctly.")}
```

# Augment Checking

### SEE MY NOTE IN THE EMAIL

**Check distribution of Augment marketer_code by cell_code. Does it align
with previous month?** *(This may have to be a manual check. I can probably
pull the distribution from the previous month in the future once this
script has been utilized for one month and I have the output)*

```{r}
augment <- augment %>% filter(!marketer_code %in% c("", "SP138", "SP139")) %>% 
  mutate(customer_id = gmpi_base_cust_id %>% as.numeric())

cell_code_naw_sp_ct <- augment %>% 
  freq_table(c("naw_cell_code", "cell_code", "marketer_code"), 
             caption="Naw Cell Code vs Cell Code vs Sp Code Frequencies")
```

```{r}
# Check if someone in the augmented file is in the open segment file
open_seg_check_aug <- augment %>% 
  inner_join(open_seg, by = c("gmpi_base_cust_id", "customer_id"))

if (nrow(open_seg_check_aug) > 0){
  warning("Customers in the augmented file appear in the new segment file")
  cat('\n')
  if (nrow(open_seg_check_aug) > 3000){
    warning("More than 3000 augmented file customers appear in the new segment. REPORT")
  } else{
   message("Less than 3000 augmented file customers appear in the new segment. Note and explain these customers. No need to report")
  }
} else{
  message("SUCCESS: No augmented file customers appear in the new segment")
}
```

### Check the Frequencies of the Augment Data

-   Checking expected specs to actual specs for augmented data.

-   Expected specs found in `Sample_Prep_Helper.xlsx` sheet *Augment_Specs*

-   Check tenure category and var Frequency to make sure they align with
    the expected specs

    -   Note errors

```{r message=FALSE}
exp_cell_codes <- read_excel(SAMPLE_PREP_PATH,
                             sheet = "Augment_Specs")
```

```{r}
# Check ranges of tenure and spend for augment cells
augment <- augment %>% 
  left_join(open_seg, by = c("gmpi_base_cust_id", "customer_id"))

tv_ncc_check <- augment %>% 
  group_by_summary_table("naw_cell_code", "tenure_var") %>% 
  inner_join(exp_cell_codes, by="naw_cell_code") %>% 
  dplyr::select(naw_cell_code, min, tenure_var_min, max,tenure_var_max) %>% 
  mutate(tenure_var_max = if_else(is.na(tenure_var_max), Inf, tenure_var_max),
         min_not_okay = min < tenure_var_min,
         max_not_okay = max > tenure_var_max) 

tv_ncc_tab <- tv_ncc_check %>%
  make_nice_table("Tenure Var by Naw Cell Code")

# Check if augment cell tenure and spends are within expected ranges
if (sum(tv_ncc_check$min_not_okay) > 0){
  for (ncc in tv_ncc_check$naw_cell_code[tv_ncc_check$min_not_okay]){
    warning("Minimum Tenure not correct for {ncc}" %>% f_str())
    cat("\n")
  } 
} else{
    message("SUCCESS: Minimum tenures are as expected for all codes")
}

if (sum(tv_ncc_check$max_not_okay) > 0){
  for (ncc in tv_ncc_check$naw_cell_code[tv_ncc_check$max_not_okay]){
    warning("Maximum Tenure not correct for {ncc}" %>% f_str())
    cat("\n")} 
  } else{
    message("SUCCESS: Maximum tenures are as expected for all codes")
}
```

```{r}
ten_cat_naw_cell <- augment %>% 
  group_by_summary_table("naw_cell_code", "tenure_cat") %>%
  make_nice_table("Tenure Category by Naw Cell Code")
```

-   Check the Spend Frequency for each Augment to make sure they align with
    the expected specs

    -   **Note errors**

```{r}
acct_spend_ncc_check <- open_seg_check_aug %>% 
  group_by_summary_table("naw_cell_code", "account_spend") %>%
  inner_join(exp_cell_codes, by = "naw_cell_code") %>% 
  mutate(bad_spend = (min == 0 & min_spend == ">$0")) %>% 
  dplyr::select(naw_cell_code, min, min_spend, bad_spend)

acct_spend_ncc <- acct_spend_ncc_check %>% 
  make_nice_table("Account Spend by Naw Cell Code")

if (sum(acct_spend_ncc_check$bad_spend) > 0){
  for (ncc in acct_spend_ncc_check$naw_cell_code[acct_spend_ncc_check$bad_spend]){
    warning("Minimum spend not met for {ncc}" %>% f_str())
    cat("\n")} 
  } else{
    message("SUCCESS: Minimum spend met for all codes")
}
```

-   This part of the code flags people for deletion for various reasons as
    well as noting any other change. month to month as needed.

-   The definition of the 'Flag_To' variable may change from month to month
    in order to address various problems.

-   CURRENT FLAG_TO DEFINITION

    -   1 = Delete because Wrong Sp Code in Augment

    -   2 = Delete because High Tenure in Augment

    -   3 = Delete because Spend not > $0 in Augment

-   **THERE WAS NO CODE IN SAS FOR CASE 1**

-   All instances with flags will be exported to the
    `Tenure_or_Spend_Flagged_{MONTH}_{YEAR}.csv` in the
    `Files_to_send` folder

```{r FLAG DELETION}
augment <- augment %>% 
  mutate(
    flag_to = case_when(
      # Tenure Checks
      # If anyone fails this, check with Caroline
          # we think this should actually be 2 months*/
      ((naw_cell_code == "CELL14") & (tenure_var <  5)) |
      ((naw_cell_code == "CELL18") & (tenure_var > 15)) |
      #((naw_cell_code == "CELL66") & (tenure_var <  3)) |
      ((naw_cell_code == "CELL21") & (tenure_var > 15)) |
      ((naw_cell_code == "CELL22") & (tenure_var > 15)) |
      #((naw_cell_code == "CELL53") & (tenure_var > 15)) |
      ((naw_cell_code == "CELL35") & (tenure_var >  4)) ~ 2, #|
      #((naw_cell_code == "CELL67") & (tenure_var >  4)) ~ 2,
      
      # Spend Checks
      ((naw_cell_code == "CELL21") & (account_spend <= 0)) ~3 #|
      #((naw_cell_code == "CELL66") & (account_spend == 0)) |
      #((naw_cell_code == "CELL67") & (account_spend == 0)) |
      #((naw_cell_code == "CELL68") &
         # (marketer_code %in% c('SP111','SP112',
         #                       'SP113','SP114',
         #                       'SP115','SP117',
         #                       'SP118','SP123',
         #                       'SP127','SP132',
         #                       'SP136','SP145',
         #                       'SP153','SP156')) &
         # (account_spend == 0)) ~ 3
    )
  ) %>% arrange(flag_to)


# identify flagged observations
flags_only <- augment %>% drop_na(flag_to) %>% 
  dplyr::select(gmpi_base_cust_id, naw_cell_code, tenure_var, 
                      account_spend, marketer_code, setup_dt, flag_to) 

flags_only %>% 
  write_csv(f_str("../Files_to_send/Tenure_or_Spend_Flagged_{MONTH}_{YEAR}.csv"))

n_flags <- nrow(flags_only)
if (n_flags > 0){
  warning("There are {n_flags} people flagged for deletion" %>% f_str())
  cat("\n")
  warning("Find specifics in file `Tenure_or_Spend_Flagged_{MONTH}_{YEAR}.csv` in the Files_to_send folder" %>% f_str())
  
  flag_freqs <- flags_only %>% freq_table("flag_to", "Flag Freqs")
} else{
  message("SUCCESS: No one is flagged for deletion")
}
```

```{r Remove Flagged Observations}

# If approved, run this line to remove the flagged observations
augment <- augment %>% filter(is.na(flag_to))
```


```{r SUBJECT LINE}
# perform ab split (if desired)
# makes new variables based on split
augment <- augment %>% 
  #create_ab_split(strat_var = 'marketer_code', sample_size = 0.5) %>% # Stratify sample 50% of obs for each marketer code
  mutate(selected = 0) %>% # comment this out if using the ab_split
  mutate(sp_code = parse_number(marketer_code),
         mv_nps_ind = if_else(selected == 0, "NPS", "MV"),
         mr_in_n = if_else(mr_in == 'Y', 1, 2),
         subject_line = if_else(selected == 0, 6, 7)) %>% # Change the definition of subject_line according to this month's instruction
  select(-flag_to)
ncc_mv_nps <- augment %>% freq_table(c("naw_cell_code", "mv_nps_ind"),
                          "naw cell code vs MV NPS IND Freqs")
```

```{r}
sel_sbj_line <- augment %>%
  freq_table(c("selected", "subject_line"), "Selected vs Subject Line Freqs")
```

```{r}
# Store important sample datasets for weighting step
save(augment, main, file=f_str("../Data/unweighted_samples_{MONTH}_{YEAR}.Rdata"))
```

```{r message=FALSE}
# IF YOU ARE RUNNING `USCS_Weighting.Rmd` right after this, run this chunk and then you DO NOT have to reload in the data with the step `load(f_str("../Data/unweighted_samples_{MONTH}_{YEAR}.Rdata"))`
# There's no harm if you do, but the dataframes you need will stay in your environment

rm.all.but(keep = c('main', 'augment'))
```
